\bigskip GRASS GIS Vector State of the Art - Gearing towards GRASS GIS 7 \bigskip

### 2014-04-10 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: add which texlive packages are needed
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59667 15284696-431f-4ddb-bdfa-cd5b030d7da7
Added some figures from Martin's PhD
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59672 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
% not needed:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Linear features extraction}{
\small
blabla
\begin{center}
 %\includegraphics[width=0.48\textwidth]{./images/imagery_spot_original}
 %\hspace{10mm}
 %\includegraphics[width=0.48\textwidth]{./images/imagery_spot_edge_1}
 %\newline
 Figure 1: Canny edge detector on a road network [2]
\end{center}
}

@@

\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
\scriptsize
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005. 
International Journal of Geoinformatics, 1(1): 51-61.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Interactive supervised classification}{
This
\begin{center}
 %\includegraphics[width=0.47\textwidth]{./images/wxiclass1.png}
 %\newline
 Figure 3: Interactive image classification with coincidence plots (left side) \& histograms (right side)
\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Satellite imagery products}{
blabla
}

@@

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Multi- and hyperspectral data analysis}{
\smallskip
Unmixing

\begin{center}
 %\includegraphics[width=0.4\textwidth]{./images/unmix_pixels_spectrum.pdf}
 %\newline
 Figure 7: Unmixing principle (left), end-members selection (right), error space (below)
\end{center}
}

>>>>

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
% needed for authors:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Topology support}{
\small
blabla
\begin{center}
 \includegraphics[width=0.48\textwidth]{./svg_images/grass6-topo}
 \hspace{10mm}
 \includegraphics[width=0.48\textwidth]{./svg_images/grass7-topo}
 \newline
 Figure 1: Topology changes from version 6 to 7 after [5]
\end{center}
}

@@

\blocknodew[($(funkcionalita)+(20,-1)$)]{35}{References}{
\scriptsize
\begin{center}
\begin{tabular}{rp{0.9\textwidth}}
[1] & Neteler \& Bowman \&  Landa \& Metz, 2012. Environment \& Modeling Software, 31:124-130\\{}
[2] & Petráš, 2012. M.Sc. Thesis, OSGeoREL, FCE CTU, Prague.\\{}
[3] & Kratochvílová \& Petráš, 2013. OSGeoREL, FCE CTU, Prague.\\{}
[4] & Neteler \& Grasso \& Michelazzi \& Miori \& Merler \& Furlanello, 2005.\\{}
[5] & Landa, 2013. PhD thesis, CTU, Czech Republic.
International Journal of Geoinformatics, 1(1): 51-61.
\end{tabular}
\end{center}
\smallskip
\hrulefill
\vspace{-5pt}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Data Sources}{
This
\begin{center}
 \includegraphics[width=0.47\textwidth]{./images/grass-data-sources}
  \newline
 Figure 3: Data sources
\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Topology structure}{

\begin{center}
 \includegraphics[width=0.47\textwidth]{./images/topo-geo-grass}
  \newline
 Figure 3: Topology structure
\end{center}
}

@@

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{3D}{
\smallskip
Unmixing

\begin{center}
 \includegraphics[width=0.4\textwidth]{./images/grass7-3d}
 \newline
 Figure 7: 3D handling
\end{center}
}
